Covering Your Basis: Model Agnostic Probes of the Binary Black Hole Population

### 2022-09-26 src/tex/results.tex
move macros

@@

>>>>

MSpline IID:
$\cos{\theta}_\mathrm{max} = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][peakCosTilt]}$}
$\gamma = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][log10gammaFrac]}$}
$f_{<0} = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][negFrac]}$}
MSpline Independent:
$\cos{\theta_1}_\mathrm{max} = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][peakCosTilt1]}$} and $\cos{\theta_2}_\mathrm{max} = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][peakCosTilt2]}$}
$\gamma_1 = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][log10gammaFrac1]}$} and $\gamma_2 = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][log10gammaFrac2]}$} 
$f_{1,<0} = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac1]}$} andand $f_{2,<0} = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac2]}$}

@@

Default: $f_{\chi_\mathrm{eff}<-0.3} = $\result{$\CIPlusMinus{\macros[ChiEffective][default][FracBelowNeg0p3]}$} 
$f_{\chi_\mathrm{eff}<0} = $\result{$\CIPlusMinus{\macros[ChiEffective][default][FracBelow0]}$} 
$\chi_\mathrm{eff, peak} = $\result{$\CIPlusMinus{\macros[ChiEffective][default][PeakChiEff]}$}

MSplineIID: $f_{\chi_\mathrm{eff}<-0.3} = $\result{$\CIPlusMinus{\macros[ChiEffective][iid][FracBelowNeg0p3]}$}
   $f_{\chi_\mathrm{eff}<0} = $\result{$\CIPlusMinus{\macros[ChiEffective][iid][FracBelow0]}$} 
   $\chi_\mathrm{eff, peak} = $\result{$\CIPlusMinus{\macros[ChiEffective][iid][PeakChiEff]}$}

MSplineIND: $f_{\chi_\mathrm{eff}<-0.3} = $\result{$\CIPlusMinus{\macros[ChiEffective][ind][FracBelowNeg0p3]}$}
   $f_{\chi_\mathrm{eff}<0} = $\result{$\CIPlusMinus{\macros[ChiEffective][ind][FracBelow0]}$} 
   $\chi_\mathrm{eff, peak} = $\result{$\CIPlusMinus{\macros[ChiEffective][ind][PeakChiEff]}$}

MSplineChiEff: $f_{\chi_\mathrm{eff}<-0.3} = $\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelowNeg0p3]}$}
      $f_{\chi_\mathrm{eff}<0} = $\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelow0]}$} 
      $\chi_\mathrm{eff, peak} = $\result{$\CIPlusMinus{\macros[ChiEffective][chieff][PeakChiEff]}$}
